
\documentclass[preprint,authoryear]{elsarticle}\frenchspacing

\usepackage{linguex}
\usepackage{qtree}
\qtreecenterfalse
\usepackage{tree-dvips}
\usepackage{phonetic}
\usepackage{xcolor}
\usepackage{pifont}
\usepackage{lineno}
\usepackage{graphicx}
%\usepackage{qdotbranch}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{CJK}
\usepackage{tikz}
\usepackage{amsfonts} 

\def\url#1{\expandafter\string\csname #1\endcsname}

\definecolor{Blue}{RGB}{0,0,255}
\newcommand{\jd}[1]{\textcolor{Blue}{[jd: #1]}}  
\newcommand{\gcs}[1]{\textcolor{blue}{[gcs: #1]}}  


\newcommand{\sem}[1]{\mbox{$[\![$#1$]\!]$}}
\newcommand{\type}[1]{\ensuremath{\left \langle #1 \right \rangle }}
\newcommand{\lam}{\ensuremath{\lambda}}

\renewcommand{\firstrefdash}{}

\begin{document}
\frenchspacing 


\journal{Semantics and Pragmatics}
%\journal{Linguistic Inquiry}

\begin{frontmatter}

\title{On the grammatical source of adjective ordering preferences} 

%\author{\textcolor{white}{Anonymous}}

\author[irvine]{Gregory Scontras\corref{cor1}}
\ead{g.scontras@uci.edu}
\ead[url]{http://linguistics.uci.edu/scontras/}

\author[stanford]{Judith Degen}

\author[stanford]{Noah D.~Goodman}

\address[irvine]{University of California, Irvine}


%\author{Judith Degen}
\address[stanford]{Stanford University}


\cortext[cor1]{Corresponding author}


\begin{abstract}
 \cite{scontrasetal2017adjectives} present experimental evidence demonstrating that the best predictor of adjective ordering preferences in the English noun phrase is the subjectivity of the property named by any given adjective: less subjective adjectives are preferred linearly closer to the nouns they modify. The current work builds on this empirical finding by proposing that the reason subjectivity predicts adjective ordering preferences has to do with the hierarchical structure of nominal modification. Adjectives that are linearly closer to the modified noun are often structurally closer, composing with the noun before adjectives that are farther away. Pressures from successful reference resolution dictate that less subjective, more useful adjectives contribute their meaning to the resulting nominal earlier, in an attempt to more effectively limit the reference search space.
\end{abstract}

\begin{keyword}
adjective ordering, subjectivity, hierarchical structure, modification, reference resolution
\end{keyword}

\end{frontmatter}

\noindent Word count: 5634

\section{Introduction}

Adjective ordering preferences determine the relative order of adjectives in multi-adjective strings. Such preferences dictate that \emph{the small brown cardboard box} sounds much more natural than \emph{the brown cardboard small box}, or any other ordering of the adjectives. 
These preferences are robustly attested, not only in English, but in a host of additional, unrelated languages \citep{dixon1982,hetzron1978,lapollahuang2004,martin1969competence,sproatshih1991}. Remarkably, the \emph{same} preferences surface in each case. Even more remarkably, in post-nominal languages where adjectives follow the nouns they modify, the preferences are the mirror image of what are found in pre-nominal languages like English \citep{dixon1982,hetzron1978,sproatshih1991}; at issue is the relative distance of an adjective from the noun it modifies.

Given their stability within and across languages, a glaring question presents itself: what factors determine these robust preferences? Answers to this question stand to inform not only the preferences themselves, but also the psychological and grammatical systems from which these preferences emerge. For this reason, adjective ordering preferences have been the subject of targeted inquiry since \cite{sweet1898} wrote about them over a century ago. Hypotheses abound, ranging from the psychological \citep{sweet1898,whorf1945,ziff1960,martin1969} to the grammatical \citep{cinque1994,scott2002,laenzlinger2005,mcnallyboleda2004,svenonius2008,truswell2009}. Still, significant progress has proven elusive, owing to the complex, careful empirical work required to test these hypotheses.

Recently, \cite{scontrasetal2017adjectives} brought behavioral and corpus data to bear on the question of adjective ordering. Distilling the proposals that preceded them, \citeauthor{scontrasetal2017adjectives} advanced the hypotheses that property subjectivity determines the relative order of adjectives in multi-adjective strings, such that less subjective adjectives occur linearly closer to the nouns they modify (see also \citealp{quirketal1985,hetzron1978,dixon1982,tucker1998,hill2012}). In \emph{the small brown cardboard box}, \emph{cardboard} is much less subjective than \emph{brown} or \emph{small}, so \emph{cardboard} is preferred closer to the modified noun.

With strong empirical footing for the factor determining ordering preferences, the question now shifts to precisely \emph{why} subjectivity should play such a central role in adjectival modification. The remainder of this short paper proceeds as follows. Section \ref{review} reviews the empirical methodology and findings from \cite{scontrasetal2017adjectives}. Section \ref{why} explores potential explanations of the empirical findings. Section \ref{proposal} offers a proposal tying subjectivity to reference resolution and the hierarchical structure of adjectival modification. Section \ref{conclusion} concludes.


\section{Subjectivity predicts adjective ordering preferences} \label{review}

To identify the factors at play in adjective ordering preferences, we must first determine what the preferences are that need explaining. To that end, \cite{scontrasetal2017adjectives} began their study by establishing a behavioral measure of ordering preferences. They asked experimental participants to indicate the preferred ordering of adjectives in adjective-adjective-noun strings (e.g., \emph{the small brown chair} vs.~\emph{the brown small chair}). From these relative preferences the authors then calculated a single preferred-distance measure for each adjective tested, corresponding to that adjective's overall proximity to modified nouns. The authors evaluated their behavioral proximity measure against naturalistic productions from English corpora. Finding an extremely strong correlation between the behavioral measure and the corpus counts, the authors concluded 1) that naive speakers have reliable and robust adjective ordering preferences, and 2) that the behavioral measure faithfully captured these preferences. With a clear handle on the preferences, the authors then shifted their focus to the aspect of adjective meaning that they hypothesized best predicted ordering preferences: subjectivity. 

Inspired by the various proposals about aspects of adjective meaning explaining their relative order in multi-adjective strings, \citeauthor{scontrasetal2017adjectives} distilled past proposals into the intuitive psychological construct of subjectivity. Crucially, the authors \emph{operationalized} their subjectivity hypothesis as a behavioral measure for the purpose of empirical testing. Adjective subjectivity was measured by asking participants how ``subjective'' a given adjective was. These raw ``subjectivity'' scores were evaluated against a potentially more ecologically valid method: faultless disagreement \citep{kolbel2004,barker2013,kennedy2013,macfarlane2014}. To the extent that two speakers can disagree about a given property for an object without one speaker necessarily being wrong (e.g., disagreeing about whether or not a box counts as small), the property admits that degree of faultless disagreement, which stands proxy for the adjective's subjectivity. Finding extremely high correlations between the ``subjectivity'' scores and the faultless disagreement measure, \citeauthor{scontrasetal2017adjectives} concluded that both measures successfully capture adjective subjectivity.

\gcs{note on our operationalization of subjectivity and the various semantic factors that contribute to it} It bears noting that many factors can contribute to the perceived subjectivity of an adjective, including semantic notions typically thought of as vagueness (e.g., beautiful in which sense?) or relativeness (e.g., large compared to what?) or context dependence XXX. Moreover, there exist a variety of semantic theories designed to account for these specific notions (e.g., the perspectives of \citealt{kolbel2002} or the judges of \citealt{lasersohn2005} \gcs{kamp and partee 1995}). For our purposes and the purposes of \citeauthor{scontrasetal2017adjectives}'s study, the semantic source of subjectivity runs orthogonal to the simple fact that speakers have stable estimates of subjectivity operationalized via faultless disagreement. In other words, whatever its source, language users recognize that certain adjectives can lead more frequently to cases of misalignment where people might (faultlessly) disagree about the set of things picked out by a given adjective.

With clear estimates of adjective subjectivity and of the preferences themselves, the authors then tested the predictive power of subjectivity in explaining ordering preferences. Recall the hypothesis: adjectives with lower subjectivity scores are preferred linearly closer to the nouns they modify. Indeed, this is precisely what \citeauthor{scontrasetal2017adjectives} found: an adjective's semantics predicts its distance from the nouns it modifies, with subjectivity scores accounting for nearly all of the variance in the ordering preference data. Moreover, preference strength increased with the subjectivity differential. To get a clearer picture of the \emph{relative} success of their subjectivity hypothesis, the authors then compared the predictions of subjectivity against operationalizations of competing proposals: adjective inherentness (whereby adjectives with more ``essential'' meanings occur closer to modified nouns; \citealp{sweet1898,whorf1945,ziff1960}), intersective vs. subsective modification (whereby intersective modifiers compose first in the hierarchical structure of nominals; \citealp{truswell2009}), and concept formability (whereby adjectives that form complex, idiomatic concepts compose early; \citealp{bouchard2005, mcnallyboleda2004, svenonius2008}). In each case, subjectivity continued to be a better predictor of ordering preferences.


\section{Why subjectivity?} \label{why}

Finding subjectivity to be a reliable and robust predictor, our task now is to explain why subjectivity should determine adjective ordering preferences: why should less subjective adjectives be preferred linearly closer to the nouns they modify? \citeauthor{scontrasetal2017adjectives} hint at an answer in the discussion of their results, namely pressure from successful reference resolution. Before reviewing their discussion, it will be useful to first consider the range of possible answers to this \emph{why} question. In the process, we also establish desiderata for successful answers.

To begin, we might propose that the observed subjectivity gradient emerges from a rigid syntax of adjectival modification: adjectives inhabit specialized syntactic projections depending on their semantic class (e.g., Color Phrase for color adjectives, Shape Phrase for shape adjectives, etc.; \citealp{cinque1994,scott2002,laenzlinger2005}), and these projections happen to order in a way that tracks subjectivity. While a cartographic approach along these lines might help to explain the observed behavior, it leaves unanswered the question of \emph{why} subjectivity should matter in the ordering of adjectival projections. Also problematic is the rigidity introduced by a syntax that allows only one ordering for any string of adjectives. This rigidity predicts categorical ordering preferences, yet \citeauthor{scontrasetal2017adjectives} observed graded judgments that track differential subjectivity. Thus, a cartographic syntax appears to be a nonstarter for explaining why subjectivity should predict ordering preferences.

Shifting our sights to psychological explanations, we might try to account for the role of subjectivity by making appeal to the relative salience of properties for the nouns they modify. Properties that are more salient---more \emph{inherent} to the objects described by the noun \citep{sweet1898,whorf1945,biberetal1999}---ought to be more accessible in the construction of nominals. An account based on the accessibility of adjectives during the on-line construction of nominal phrases stands to extend straightforwardly to languages with post-nominal adjectives where the preferences are preserved in the reverse: phrases are built outward from their heads, so more accessible adjectives occur linearly closer to the head of the nominal construction: the noun. The leap that must be made, however, links subjectivity to inherentness and thereby to accessibility. Unfortunately, this leap appears untenable. \citeauthor{scontrasetal2017adjectives} measured adjective inherentness and compared its predictions with those of subjectivity. Whereas subjectivity accounted for at least 75\% of the variance in the ordering preferences, inherentness accounted for 0\%. While an explanation in terms of adjective accessibility might still prove promising, the implementation via inherentness lacks empirical support.

Rather than inherentness, we might try tying adjective accessibility to adjective frequency, such that more frequent adjectives are more accessible during the hierarchical construction of nominal phrases. To account for the role of subjectivity, we would expect more frequent---and thus more accessible---adjectives to have lower subjectivity scores. \citeauthor{scontrasetal2017adjectives} investigated the role of adjective frequency in ordering preferences, finding it to be a significant predictor. However, frequency applies pressure in the direction opposite to what we have been considering: in English, more frequent adjectives occur \emph{farther} from the modified noun because they occur \emph{linearly} early in multi-adjective strings \citep[cf.][]{bock1982,wulff2003}. 
Moreover, the authors found that subjectivity continues to explain significant variance in the preferences over and above adjective frequency. While frequency likely contributes to the relative accessibility of adjectives during the construction of nominal phrases, its contribution is separate from that of subjectivity; the two forces work in tandem and in opposite directions. %We can see the two pressures pull apart once we consider specific examples. Material adjectives like \emph{wooden} or \emph{metal} were found to be the least subjective in \citeauthor{scontrasetal2017adjectives}'s study; value adjectives like \emph{good} and \emph{bad} were the most subjective.   Thus, accessibility by frequency does little to explain why subjectivity should play such a central role.

We find perhaps the most thought-through version of the psychological accessibility hypothesis in \citeauthor{martin1969competence}'s (\citeyear{martin1969competence}) experimental investigations. Inspired by prior results demonstrating the predictive power of ``definiteness of denotation'' in adjective ordering preferences \citep{martin1969}, \citeauthor{martin1969competence} set out to test the hypothesis that adjectives occurring linearly closer to nouns indeed are more accessible. Participants completed a series of elicited production tasks in which they were shown visual arrays of objects and asked to name specific properties of the objects they saw (e.g., size vs.~color). There were two versions of the experiments: one for English speakers, and another for speakers of Indonesian, a post-nominal language with the mirror image of the English ordering preferences. By measuring production latencies, \citeauthor{martin1969competence} discovered that adjectives preferred linearly closer to nouns are produced more quickly. From this he concluded that adjectives closer to the noun are more accessible than adjectives preferred farther away. 

Before accepting \citeauthor{martin1969competence}'s results as unambiguous support for an adjective accessibility hypothesis, we must confront two issues. First, production latencies in context likely depend on more than the relative accessibility of words from memory; how can we be sure that the observed differences in latencies did not derive from low-level properties of the visual displays? If the issue at play is truly the \emph{lexical} accessibility of adjectives, then the displays should have controlled for the relative perceptual salience of the properties being named. As things stand, we have no way of teasing apart lexical accessibility from visual salience in \citeauthor{martin1969competence}'s results.
%If ordering preferences depend on the relative salience of various adjectives during the on-line construction of a nominal phrase, then there should be contexts in which canonical orderings are reversed. 
Second, if accessibility truly determines adjective ordering preferences, why should adjective frequency apply pressure in the opposite direction? Relative frequency surely determines adjective accessibility, and we saw above that adjective frequency is a significant predictor of ordering preferences. However, more frequent adjectives are preferred early in the linear structure of nominal phrases, not closer to the nominal head (at least not in pre-nominal languages like English). Accessibility as measured by adjective frequency seems to be delivering the wrong predictions.


%% MARTIN 1969 COMPETENCE
%"it is hypothesized that the left-to-right order of morphemes in the bases corresponds to the habitual real time order of choice of these morphemes."
%"it is hypothesized that the left-to- ight reordering of morphemes by transform- ations corresponds to the habitual reordering of those morphemes in real time for pro- duction"
%"It is therefore proposed that speakers of English and Indonesian habitually choose adjectives after choosing the modified nouns"
%"in English, preferred adjective order should correlate negatively with the order of adjective choice and, in Indonesian, the correlation should be positive."
%"adjectives preferred close to the noun are generally
%capable of stronger associations with the noun"
%"produce the appropriate value for the dimension presented to them as quickly as possible. Thus, if they had been instructed to attend to LARGE RED CIRCLE and had been given the word size, it was their task to respond with the word large as quickly as possible. By recording the latencies of these encoding responses, it was possible to determine the relative accessibilities of the adjectives involved."
%"Lockhart and Martin have shown that the adjectives which are expressed first in English are less available for recall than those which are expressed later."
%Adjectives closer to the noun are more "Accessible"

%% MARTIN 1969 DETERMINANTS
%"the proper choice of an adjective often depends on a relation- ship between the meaning of the modified noun and the property to be denoted by the adjective"
%"adjectives differ in the degree to which the noun context must be considered in the choice of adjectives"
%"The accessibility of adjectives is hypothesized to depend, in part, on the degree to which their choice is constrained by the meaning of the modified noun. In the choice of those adjectives which are context inde- pendent in denotations, less time is thought to be required for scanning the meaning of the modified noun than in the choice of adjectives which are context-sensitive in denotation."
% This is really just codifying the intersective vs. subsective distinction
%"If an adjective is frequently used in many different contexts, its user will be more sensi- tive to the ways in which its meaning is affected by noun context than if the adjective is infrequently used."
%"when Ss were given ample time to judge the definite- ness or absoluteness of adjectives, frequency did not significantly correlate with those judgments"


There of course remains the possibility that adjective accessibility is not the primary link between subjectivity and ordering preferences. In an attempt to tie properties of language structure to general principles of cognition, \cite{bever1970} advanced the hypothesis that structural norms---among them, adjective ordering preferences---emerge from the human perceptual system. To see how perception could determine the preferred ordering of a string of adjectives, one must appreciate the task of the parser, at least as envisaged by \citeauthor{bever1970}. Upon encountering the speech stream, the parser relies on various heuristics to efficiently identify constituents and associate them with an appropriate argument structure. In service of this task, the parser needs an identification mechanism for noun phrases: where do they begin, and where do they end? 

According to \citeauthor{bever1970}, the more ``nounlike'' the adjective, the closer it appears to the modified noun \citep[see also][]{biberetal1999,posner1986}. Returning to the small brown cardboard box, \emph{cardboard} is the most felicitous when used as a noun, \emph{brown} slightly less so, and \emph{small} the least of all (cf.~\citeauthor{bever1970}'s examples (68) and (69)). 
%(modified from \citeauthor{bever1970}'s examples (68) and (69)):
%
%\ex. \a. Brown is a color.
%\b. Cardboard is a material.
%\b. *That box is made out of brown.
%\b. That box is made out of cardboard.
%\b. *The brown broke.
%\b. The cardboard broke.
%
%\ex. \a. Brown is my favorite color.
%\b. *Small is my favorite size.
%\b. He splattered some brown on me.
%\b. *He splattered some small on me.
%\b. Brown and blue and green are colors.
%\b. ?Small and large and enormous are sizes.
%
Now, why should ordering adjectives according to their nounlike character ease the burden of the parser in its search for noun phrase boundaries? \citeauthor{bever1970} proposes that a linear parser identifies the beginning of a noun phrase with the presence of a determiner. That same parser identifies the right edge of the noun phrase with the transition from a clearly nounlike element to a lexical item that is ``less uniquely a noun'' \citep[p.~323]{bever1970}. In other words, the primary cue to the right edge of a noun phrase is a salient decrease in nounlike character. If adjectives were randomly ordered with respect to their nounlike character, the parser might mistakenly identify noun phrase boundaries, as in [\emph{the cardboard}] [\emph{brown box}]. These early errors identifying phrase boundaries would cascade into a total failure for the sentence parse.

\citeauthor{bever1970}'s proposal offers an intuitive explanation of the pressures that determine pre-nominal adjective ordering, and it might extend to handle the mirror-image preferences in post-nominal languages---though the details would need to be carefully thought through. The proposal even offers a promising connection to subjectivity: perhaps less subjective adjectives yield more-well-defined categories, which are more amenable to naming with nouns. Thus, subjectivity determines nounlike character, and nounlike character determines relative order in multi-adjective strings. Unfortunately, \citeauthor{bever1970}'s proposal suffers a serious flaw: it lacks empirical support. In her corpus analysis of English ordering preferences, \cite{wulff2003} %p.255
calculated nounlike character for a host of adjectives and demonstrated that it does little by way of predicting adjective order. What effect nounlike character does have on the linear order of adjectives applies pressure in the direction opposite of \citeauthor{bever1970}'s hypothesis: more nounlike adjectives are marginally more likely to occur \emph{farther} from the modified noun \citep[p.~255]{wulff2003}.

It would appear that we have arrived at an impasse: accessibility-based accounts struggle to explain the full range of data from both pre- and post-nominal languages; they also face a serious obstacle in the form of lexical frequencies. \citeauthor{bever1970}'s perception-based account seems well-suited for pre- and post-nominal languages, but \citeauthor{wulff2003}'s facts suggest the proposal is misguided. And all of these proposals lack a clear connection to adjective subjectivity. There remains another strategy, however, which shifts the explanation from how language users use adjectives to what adjectives do for language users. As we shall see, a functional account along these lines stands the best chance of explaining the role of subjectivity in determining ordering preferences.

For \cite{seiler1978}, the clue to understanding adjective ordering preferences lies in the task that adjectives perform: determination. Noun phrases are inherently referential, whether to real-world objects or to well-defined concepts. In either case, determiners in the broad sense---demonstratives, articles, numerals, quantifiers, adjectives, prepositional attributes, relative clauses---contribute to nominal meaning in service of pinning down a referent. With this function in mind, \citeauthor{seiler1978} identifies regularities in the linear order of determiners. First, ``the range of head nouns for which a determiner D is potentially applicable increases with the positional distance of that determiner from the head noun N'' \citep[p.~308]{seiler1978}. For the purposes of adjective ordering, the more nouns an adjective can felicitously describe, the farther that adjective will appear from the noun. \citeauthor{seiler1978} explicitly links determiner applicability with property inherentness: less broadly-applicable, more special-purpose adjectives name properties that are more inherent to the modified noun. He gives the example of \emph{rote h\"{o}lzerne Kugeln} `red wooden balls':

\begin{quotation}The semantic structure of \emph{Kugeln} qua solid objects naturally implies material constitution of some sort; it implies---with a lesser degree of naturalness---some property in the color spectrum. To this gradient decrease in natural semantic implication corresponds the normal word order in which the `determiner' with the strongly implied property is closer to the head noun than the `determiner' with the less strongly implied property. \citep[p.~309]{seiler1978}\end{quotation}

Properties implied by the nominal have meanings that are at least partially contained already within the nominal meaning, hence the implication (cf.~the notion of mutual informativity; \citealp{futrell2017}). Determiners that are less implied by the nominal will be more informative (i.e., unexpected) when encountered, with greater informativity leading to a greater potential of pinning down the intended referent.  Thus, according to \citeauthor{seiler1978}, ``the potential of a determiner D for singling out the object referred to by the head noun N increases proportionally with the positional distance of D from N'' \citep[p.~309]{seiler1978}. The ordering that results presumably follows from the desire to introduce the more informative, more useful elements early in the construction of a nominal.

\citeauthor{seiler1978}'s first claim---that adjectives describing a broader set of nouns appear farther from the modified noun---finds empirical support in \citeauthor{wulff2003}'s corpus analysis \citep[pp.~266--267]{wulff2003}. However, the implication of \citeauthor{seiler1978}'s second claim---that speakers introduce more useful elements (for the purpose of determination) earlier---fails in the case of post-nominal languages with mirror-image preferences. This reasoning would hold that speakers in post-nominal languages save the most useful adjectives for last, which stands in direct conflict with the explanation for pre-nominal languages. Still, we should not abandon the functional account of adjective ordering altogether. In the following section, we consider a different proposal that preserves \citeauthor{seiler1978}'s intuition that ``in order to fully understand the regularities we must look behind the mere facts and try to see the program and ultimately the purposive functions of which they are manifestations'' \citep[p.~325]{seiler1978}.

%% Seiler 1978 on ``determination''
%
%problem: mirror image preferences
%

%
%"The more widely a 'determiner' is applicable to a head noun (AI), the more it contributes to determining the reference and the less it contributes to determining the concept of the head noun (A2). The less widely applicable a 'determiner', the less it contributes to reference (AI), and the more it contributes to identifying the
%concept (A2). explicating, as it were, its inherent properties." p. 310
%
%Behagel's first law
%
%"evaluating adjectives surpass color and material adjec- tives in distance with respect to N because their specificatory function (i.e, the function which determines reference or extension) outweighs their char- acterizing function (l.e. the function which determines properties of the concept or intension)" p. 311
%
%"potential for "pinning down" a referent" p. 313
%
%"local squishiness" p.314
%
%"In order to fully understand the regularities we must look behind the mere facts and try to see the program and ultimately the purposive functions of which they are manifestations" p.325

\section{Linking subjectivity to the hierarchical structure of modification} \label{proposal}

Let us begin as \citeauthor{seiler1978} did, with the observation that adjectives aid in establishing reference. Starting with a noun like \emph{box}, potential referents include every box in the discourse context. Where there are multiple boxes, the listener's task of establishing reference amounts to a game of chance. We increase our odds of winning this game as we narrow down, or \emph{determine} the set of potential referents. Encountering an adjective like \emph{cardboard}, we now only consider the subset of boxes that are cardboard. Encountering \emph{brown}, we limit ourselves to the cardboard boxes that are brown. Encountering \emph{small}, we further limit ourselves to just those brown cardboard boxes that are small. From the set of all boxes we home in on the small brown cardboard boxes, a much smaller set indeed.

When it comes to the structure of these multi-adjective strings, we treat adjectival modification as syntactic adjunction, as in \ref{modification}. Semantically, we begin by treating modification as set intersection, where the adjective restricts the set characterized by the nominal denotation to just those elements that hold the specified property. For our purposes, it does not matter whether this intersection proceeds via a special mode of semantic composition (e.g., Predicate Modification; \citealp{heimkratzer1998}), via run-of-the-mill functional application with adjectives of a higher type \citep{parsons1970modifiers,montague1970,kamp1975,siegel1976}, or via functional structure \citep{rubin1994,scontrasnicolae2014}. In each case, semantic composition proceeds outward from the noun, with adjectives closer to the noun making their semantic contribution earlier than adjectives farther away. The resulting nominal denotation appears in \ref{denotation}, where the NP characterizes the set of small brown cardboard boxes.

\ex. \label{modification}
\Tree [.NP [.AP \emph{small} ] [.NP [.AP \emph{brown} ] [.NP [.AP \emph{cardboard} ] [.NP \emph{box} ] ] ] ] 

\ex. \label{denotation}
\sem{small brown cardboard box} = \flushright \mbox{\lam x. box(x) = cardboard(x) = brown(x) = small(x) = 1}

\begin{figure}[t]
	\centering
	\begin{tikzpicture}
	%                              \draw (-2, 1.2) rectangle (2, -2.2);
	\begin{scope}
	\clip (0, 0) circle (4);
	\fill[color=gray!45] (-5,5)
	rectangle (5,-5);    
	\end{scope}
	\begin{scope}
	\clip (0, 0) circle (3.025);
	\fill[color=gray!30] (-5,5)
	rectangle (5,-5);    
	\end{scope}
	\begin{scope}
	\clip (0, 0) circle (2);
	\fill[color=gray!15] (-5,5)
	rectangle (5,-5);    
	\end{scope}
	\begin{scope}
	\clip (0, 0) circle (1);
	\fill[color=gray!0] (-2,1.5)
	rectangle (2,-1.5);    
	\end{scope}
	\node(a) at (-0.35,.5) {\emph{small}}; %%% 3 boxes
	\node(a) at (0,-.4) {$\Box$};
	\node(a) at (0.3,.1) {$\Box$};
	\node(a) at (-0.4,0) {$\Box$};
	\node(a) at (-1,1.2) {\emph{brown}}; %%% 12 boxes
	\node(a) at (-.5,1.6) {$\Box$};
	\node(a) at (.2,1.5) {$\Box$};
	\node(a) at (.9,1.3) {$\Box$};
	\node(a) at (1.5,.7) {$\Box$};
	\node(a) at (1.3,.1) {$\Box$};
	\node(a) at (1.4,-.6) {$\Box$};
	\node(a) at (1,-1.15) {$\Box$};
	\node(a) at (0.4,-1.3) {$\Box$};
	\node(a) at (-0.4,-1.5) {$\Box$};
	\node(a) at (-0.8,-1.1) {$\Box$};
	\node(a) at (-1.4,-.6) {$\Box$};
	\node(a) at (-1.3,.2) {$\Box$};
	\node(a) at (-1.5,2) {\emph{cardboard}}; %%% 18 boxes
	\node(a) at (-2,1.2) {$\Box$};
	\node(a) at (-2.4,.6) {$\Box$};
	\node(a) at (-2.3,-.4) {$\Box$};
	\node(a) at (-2.1,-1.3) {$\Box$};
	\node(a) at (-1.8,-1.9) {$\Box$};
	\node(a) at (-1.2,-2.2) {$\Box$};
	\node(a) at (-.4,-2.5) {$\Box$};
	\node(a) at (0.4,-2.3) {$\Box$};
	\node(a) at (1.1,-2.4) {$\Box$};
	\node(a) at (1.7,-1.8) {$\Box$};
	\node(a) at (2.4,-1.1) {$\Box$};
	\node(a) at (2.6,-.3) {$\Box$};
	\node(a) at (2.3,.3) {$\Box$};
	\node(a) at (2.5,1) {$\Box$};
	\node(a) at (2,1.7) {$\Box$};
	\node(a) at (1.3,2.1) {$\Box$};
	\node(a) at (.3,2.3) {$\Box$};
	\node(a) at (-.7,2.5) {$\Box$};
	\node(a) at (-2.4,2.8) {\emph{box}}; %%% 26 boxes
	\node(a) at (-3,2.2) {$\Box$};
	\node(a) at (-3,1.3) {$\Box$};
	\node(a) at (-3.4,.6) {$\Box$};
	\node(a) at (-3.7,-.1) {$\Box$};
	\node(a) at (-3.5,-.9) {$\Box$};
	\node(a) at (-3,-1.5) {$\Box$};
	\node(a) at (-2.6,-2.3) {$\Box$};
	\node(a) at (-2,-3) {$\Box$};
	\node(a) at (-1.3,-3.4) {$\Box$};
	\node(a) at (-.6,-3.2) {$\Box$};
	\node(a) at (0.2,-3.5) {$\Box$};
	\node(a) at (1,-3.3) {$\Box$};
	\node(a) at (1.8,-3.1) {$\Box$};
	\node(a) at (2.5,-2.5) {$\Box$};
	\node(a) at (3.2,-1.8) {$\Box$};
	\node(a) at (3.1,-1) {$\Box$};
	\node(a) at (3.4,-.2) {$\Box$};
	\node(a) at (3.6,.8) {$\Box$};
	\node(a) at (3,1.5) {$\Box$};
	\node(a) at (2.6,2.2) {$\Box$};
	\node(a) at (2,3) {$\Box$};
	\node(a) at (1.2,3.2) {$\Box$};
	\node(a) at (.3,3.4) {$\Box$};
	\node(a) at (-.5,3.6) {$\Box$};
	\node(a) at (-1.2,3.1) {$\Box$};
	\node(a) at (-2,3.2) {$\Box$};
	
	\draw (0, 0) circle (1);
	\draw (0, 0) circle (2);
	\draw (0, 0) circle (3.025);
	\draw (0, 0) circle (4);
	\end{tikzpicture}
	\caption{An illustration of the restrictive modification in \emph{small brown cardboard box}.}\label{mod-fig}
\end{figure}


To see how we arrive at the denotation in \ref{denotation}, consider the illustration of this process in Figure \ref{mod-fig}. Each circle corresponds to the denotation of an NP node in \ref{modification}, with the elements ($\Box$) contained within that circle representing elements of the nominal denotation. The outermost circle represents the denotation of the smallest NP, \emph{box}. In this toy example, there are 59 boxes. Moving inward, we arrive at the next-highest NP denotation, \emph{cardboard box}; there are only 33 such boxes, so the 26 boxes that are not cardboard are pruned from the denotation. Moving inward still, we get the 15 boxes that are both brown and cardboard; the 18 non-brown cardboard boxes have been discarded. Finally, at the innermost circle, we have just those three boxes that are at once cardboard, brown, and small; the 12 brown cardboard boxes that are not small get ignored.

Thinking about the contributions of the adjectives in the example above, we notice that, for the purpose of establishing reference, different adjectives do different amounts of work. Here, ``work'' gets equated with reference-establishing potential, or potential for information gain. Measured in terms of the number of possible referents considered, more work is done by the adjectives closer to the noun. In Figure \ref{mod-fig}, \emph{cardboard} makes the largest cut in the noun's denotation, pruning 26 adjectives. Put differently, \emph{cardboard} operates over the largest set: for each of the 59 boxes, one must decide whether or not it is cardboard. Thus, there are 59 opportunities to make a mistake in this decision process, wherein a listener might misjudge a box as cardboard or not. The next adjective, \emph{brown}, makes a smaller cut, operating only over the 33 cardboard boxes; thus, there are fewer possibilities for error. The last adjective, \emph{small}, operates over the smallest set, with the smallest chance of error.

Here is the crux of the account, and finally a return to the issue of subjectivity: less subjective content is more useful for effectively communicating about the world. Encountering a relatively objective adjective like \emph{cardboard}, a listener arrives at a precise concept---one that closely aligns with that of the speaker who uttered the adjective. More subjective adjectives introduce the potential for errors in alignment, as speakers and listeners might (faultlessly) disagree about category boundaries. When it comes to ordering preferences, speakers consolidate the less subjective, more useful content around the modified noun. The claim is that they do so in an attempt to aid the listener in establishing reference by minimizing errors in alignment.

To get this story off the ground, we must consider the semantics of modification in more detail. To model the potential for faultless disagreement in subjective properties, we introduce noise into the semantics of our adjectives, as in \ref{noisy-sem}. The function \texttt{flip(x)} returns a sample from a Bernoulli distribution, where a random variable takes the value 1 with probability \texttt{x}; one can think of this function as simulating the outcome of a weighted coin flip, where heads corresponds to 1 (i.e., true) and tails corresponds to 0 (i.e., false). For our purposes, the addition of \texttt{flip()} to an adjective's semantics introduces noise at the rate $\epsilon$, where $\epsilon$ increases with subjectivity. Thus, $\epsilon_{\footnotesize\textrm{cardboard}} < \epsilon_{\footnotesize\textrm{brown}} < \epsilon_{\footnotesize\textrm{small}}$.

\ex. \label{noisy-sem}
\sem{ADJ} = \lam x. if \texttt{ADJ}(x) then \texttt{flip}($1-\epsilon$), else \texttt{flip}($\epsilon$)

Stacking a series of noisy adjectives together in a modification structure, there will indeed be a larger number of incorrect classifications (i.e., misalignments) if the adjectives are not ordered according to subjectivity. However, assuming a truly intersective semantics for modification, the probability of arriving at the correct referent once a noun has been modified does not depend on the order of the adjectives. Each adjective has some probability $p$ (i.e., $1-\epsilon$) of correctly classifying the intended object(s). Given the commutativity of noise in intersective modification, a nominal with $n$ adjectives will correctly classify the intended objects with probability $p_{adj_1} \cdot\ \ldots\ \cdot p_{adj_n}$.

We break the commutativity of noise and thus the order-independence of modification once we recognize that not all modification is intersective \citep{truswell2009,mcnally2016}. Indeed, intersective modification is likely a poor choice for adjectives like \emph{small}: asserting that Dumbo is a small elephant need not commit the speaker to the assertion that Dumbo is small. Instead, many cases of modification are subsective, such that the interpretation of the modifier (i.e., the adjective) depends crucially on the denotation of its complement (i.e., the nominal it modifies). With subsective modification in multi-adjective strings, the probability that a nominal will correctly classify its intended references \emph{does} depend on the order of adjectives: ordering relative to subjectivity will minimize potential misclassifications and thereby maximize the probability of retrieving the intended referent. In other words, once modification takes into account the content of what gets modified (as in the case of subsective modification), early errors in misclassification have the potential to get magnified. %, since later modifiers will get interpreted 

\gcs{here's an attempt at explaining how subsective modification breaks commutativity by walking through an example} Take an example with two subsective modifiers, say \emph{small old box}. Supposing that \emph{old} restricts the denotation of \emph{box} with some amount of noise $\epsilon_{\footnotesize\textrm{old}}$, the denotation of \emph{old box} will contain the intended referent with probability $1-\epsilon_{\footnotesize\textrm{old}}$. Next, \emph{small} composes subsectively by finding those old boxes that are small \emph{for old boxes}. In other words, \emph{small} examines the contents of its complement in order to fix its own interpretation. The error rate for \emph{small}, $\epsilon_{\footnotesize\textrm{small}}$, depends on the error rate that went into forming its complement, in this case $\epsilon_{\footnotesize\textrm{old}}$. As $\epsilon_{\footnotesize\textrm{old}}$ increases, so too does $\epsilon_{\footnotesize\textrm{small}}$, and thus the probability of correctly classifying the intended referent \emph{decreases}. To avoid misclassifications, one ought to use adjectives with the lowest subjectivity early in this process.

We thus see how subjectivity-based adjective ordering preferences emerge once speakers take into account the perspective of their listeners. With the goal of establishing nominal reference, less subjective adjectives are less likely to lead to errors in classification, where a listener could have a diverging opinion about whether or not some objects hold the relevant property. Although in English we encounter the reverse order, modification proceeds outward from the noun. Thus, speakers employ the most useful, least subjective adjectives early in this semantic process where there is the greatest potential for misalignment. The story works the same in languages with post-nominal adjectives where we find mirror-image preferences: linear distance corresponds to hierarchical distance, and adjectives that are closer to the noun make their semantic contributions earlier.

\gcs{note the puzzle of linear order and incremental processing}

A note of caution is in order: this account relies crucially on the assumption that a speaker's goal when using modificational content is to establish reference, yet this might not always be the case.  Consider a dialog in which Alex says to Chris, ``Do you see what he's wearing?'' Chris responds, ``What a tacky polyester shirt!'' Here, the referent (i.e., the relevant shirt) is already in common ground before Chris's utterance; the adjectives \emph{tacky} and \emph{polyester} are thus unlikely to be employed in the service of establishing reference. Instead, they communicate the speaker's stance toward the shirt in question. It remains an empirical question whether speaker goals influence ordering preferences. 
%\gcs{it wasn't clear to me what you meant by ``functional account'' here, so I opted for short and sweet} 
%\jd{i meant `functional account' in the same way that you used it above -- ie, can we figure out what the functional presssure might be that for non-referential modificational material results in the same (or favors different) ordering preferences. but i think this is fine!} % A functional account of adjective ordering in non-referential language use may turn out to reveal the same preferences; it may also turn out to reveal the reverse preferences, or no preferences at all. Working out such an account, in conjunction with attempting to derive estimates of the empirical distribution of different uses of adjectives, constitutes an important next step in evaluating the account we propose here.


Nevertheless, if we are on the right track in assuming that pressures from successful reference resolution, together with awareness of potential disagreement between speakers and listeners, lead to cross-linguistically robust adjective ordering preferences, the question turns next to how these preferences develop and how they get represented. For now we can only gesture toward possible answers. In a recent corpus analysis of child-directed and child-produced speech, \cite{barseveretal2017} documented the emergence of adult-like ordering preferences by the age of four. But are children engaging in the sophisticated theory-of-mind reasoning described above as they form these preferences? Probably not. A growing body of evidence suggests that children struggle with adult-like subjectivity awareness long after ordering preferences emerge \citep{fousheesrinivasan2017}. It would seem, then, that rather than deploying subjectivity-based heuristics, children are merely tracking and reflecting the statistics of their input, a task they are known to excel at \citep[e.g.,][]{saffranetal1996}. Children might categorize the regularities of their input according to semantic classes or adjective function, but the ultimate source of these regularities remains the careful interaction of property subjectivity with successful reference resolution. \gcs{update this discussion to accurately reflect the findings of Bar-Sever et al.}






\section{Conclusion} \label{conclusion}

Adjective subjectivity predicts adjective ordering preferences, a remarkably stable property of language design. Here we have attempted to answer the question of why subjectivity should play the role it does in these preferences. Subjective content allows for miscommunication to arise if speakers and listeners arrive at different judgments about a property description. Hence, less subjective content is more useful at communicating about the world. Speakers deploy this more useful content early in the semantic construction of nominals, as reflected in the hierarchical structure of modification: noun phrases are built semantically outward from the noun, and less subjective content enters earlier into this process. This reference-resolution account of subjectivity-based ordering preferences meets the desiderata explored in Section \ref{why}: it is predicated upon the findings of \cite{scontrasetal2017adjectives}, and so it enjoys firm empirical support. No less important, the current proposal extends seamlessly to cover the mirror-image preferences in post-nominal languages. Perhaps most appealing is the broad applicability of the proposed account: we find the same preferences cross-linguistically because communication is a central goal of language use, so pressures for successful communication apply universally.



%\section*{Acknowledgments}

\newpage

\section*{References}

\bibliographystyle{chicago}
\bibliography{greg}

\end{document}